---
title: "Toxoplasma TMT Analysis"
author: "Pierre Michel Jean Beltran"
date: "10/4/2019"
output: html_document
---
	
```{r setup}
library(ROCit)
library(plotROC)
library(tidyverse)
library(cmapR)
library(FactoMineR)
library(factoextra)
library(ggrepel)
library(pheatmap)
library(limma)
library(GGally)
library(cowplot)
library(gprofiler2)
source("helper.functions.v1.0.R")
toxo_colors = c("Exported" = "#66C2A5", "Novel PV/PVM" = "#E78AC3",
		"PV/PVM" = "#FC8D62","Non-secreted" = "#BEBADA")
toxo_shapes = c("HUMAN"=16,"Toxoplasma_gondii_GT1" = 17, "UNIQUE" = NA)
```


#Read input
```{r message=FALSE, warning=FALSE}
#Read table of observable tryptic peptides
tryp <- read_tsv("./Input/PA_UniProt.human.20171228.RISnrNF.553smORFs.264contams.Toxoplasmav43.miniTurbo.fasta.EMPAI.tsv")

#Read subcellular localization database
sl <- read_tsv("./Input/uniprot-human-cellularlocalization.txt") %>% 
	rename(accession_number = Entry, subcellular.location = 'Subcellular.location',
	       gene = 'Gene names  (primary )') %>%
	select(accession_number,subcellular.location,gene)

#Read toxoplasma annotation dataset
ta <- read_tsv("./Input/toxoplasma_locations_v2.txt")

#Read the metadata
md <- read_tsv("./Input/metadata.txt")

#Read Novel PVM Localized Proteins
novel_pvm <- read_tsv("./Input/novel_pvm_proteins_v2.txt")

#Non-secreted toxoplasma proteins
non.secreted <- read_tsv("./Input/toxoplasma_nonsecreted.txt")


#Read input files and ratio 
toxo.tsv <- read_tsv(file="./Input/toxo.tmt.sdbfrac.intensities.txt") %>% 
	filter(numPepsUnique > 1 & (species %in% c("HUMAN","UNIQUE","Toxoplasma_gondii_GT1"))) %>%
	separate("id",c("id.nodash",NA),sep = "-",remove=FALSE)%>% 
	left_join(sl,by=c('id.nodash'='accession_number')) %>% 
	left_join(ta) %>%
	left_join(non.secreted) %>%
	mutate( Location = case_when(
		accession_number %in% novel_pvm$accession_number ~ "Novel PV/PVM",
		is.na(Location) ~ "Unknown",
		T ~ Location
	))


toxo <- sm_to_gct(toxo.tsv,md,cols=1:11,join.by="sample") %>% remove_all_na()
toxo <- toxo %>% gct_ratio(1:11)
toxo@rdesc <- toxo@rdesc %>% separate("id",c("id.nodash",NA),sep = "-",remove=FALSE)


#Additional filtering criteria
toxo <- subset_gct(toxo, rid = toxo@rdesc$scoreUnique > 25 & toxo@rdesc$percentCoverage > 1 )
toxo <- subset_gct(toxo, rid = !grepl("Kerat",toxo@rdesc$entry_name))

#Median/mad normalization
toxo.norm <- toxo %>% median_mad_norm()

#Impute for proteins not quantified in 
toxo <- impute_quantile(toxo,0.01)

toxo.original <- toxo
```

#Summary statistics
```{r}
#Calculate number of proteins per species
num_toxo <- function(x){
	tox <- x %>% filter(species == "Toxoplasma_gondii_GT1") %>% nrow
	hum <- x %>% filter(species == "HUMAN") %>% nrow
	print(paste0("Counting number of proteins for dataset ", deparse(substitute(x))))
	print(paste0("Out of ", nrow(x), " proteins ", hum, " are human and ", tox," are from Toxoplasma."))
}


num_toxo(toxo.tsv)


#Calculate the number of proteins per subcellular annotation
locs <- c("Nucleus","Cytoplasm","Endoplasmic reticulum","Mitochondrion","Golgi","Cell membrane","Peroxisome")
count.locs <- numeric(length(locs))

names(count.locs) <- locs
for(i in locs){
	count.locs[i] <- grepl(i,toxo.tsv$subcellular.location) %>% sum
}

count.locs
```

#QC
```{r tmt.distributions}
#Plot density distributions for TMT intensities
toxo.melt <- melt.gct(toxo)
toxo.melt %>% ggplot(aes(x=log10(value),color=id.y)) + geom_density() + labs(x="log10(TMT intensities)") + theme_bw()
toxo.melt %>% ggplot(aes(x=log10(value),group=id.y,color=treatment)) + geom_density() + labs(x="log10(TMT intensities)") + theme_bw()

#Scatter matrix for turbo samples
subset_gct(toxo,cid = (toxo@cdesc$treatment == "turborah.toxo" | toxo@cdesc$treatment == "turborah.mock"))@mat %>% ggscatmat()

#Scatter matrix for empty samples
subset_gct(toxo,cid = (toxo@cdesc$treatment == "turborah.toxo" | toxo@cdesc$treatment == "turbocyto.toxo"))@mat %>% ggscatmat()
```

#Principal component analysis
```{r PCA.all}
toxo.nona <- toxo %>% remove_na(0)
pca.toxo <- PCA(t(toxo.nona@mat),graph=F,ncp=Inf)

fviz_eig(pca.toxo)

fviz_pca_ind(pca.toxo,col.ind = as.factor(toxo@cdesc$treatment),
	     mean.point=FALSE,geom="point",
	     addEllipses = F)+
	theme_bw()

pdf("./Figures/PCA.pdf",4.5,2.5)
fviz_pca_ind(pca.toxo,col.ind = as.factor(gsub("\\.r\\d","",toxo@cdesc$id)),
	     mean.point=FALSE,geom="point",
	     addEllipses = F)+
	theme_bw()
graphics.off()
	
```

#5. T-test analysis using limma
```{r limma.ratio.ctrl}
tr <- toxo@cdesc$treatment


#Generate the experimental model
design <- model.matrix(~ 0+ tr)

#Fit the linear model and include the calculated correlation and block structure.
fit <- lmFit(toxo@mat, design)

#Generate contrasts
contrast.matrix <- makeContrasts('turborah.vs.turbocyto' = trturborah.toxo-trturbocyto.toxo,
				 'turborah.toxo.vs.mock' = trturborah.toxo-trturborah.mock,
				 'turborah.toxo.vs.ctrl' = trturborah.toxo-trctrl,
				 'turbocyto.toxo.vs.ctrl' = trturbocyto.toxo-trctrl,
				 'turborah.toxo.vs.all' = trturborah.toxo-trturbocyto.toxo-trturborah.mock,
				 levels=design)
fit2 <- contrasts.fit(fit,contrast.matrix)

#Get BH adjusted p-values
fit.eb <- eBayes(fit2)

results <- make_nested_results(toxo,contrast.matrix,fit.eb,qval=F)
results.ratio <- make_results(toxo,contrast.matrix,fit.eb,qval=F)

map2(results$contrasts,results$data,plot_volcano)
map2(results$contrasts,results$data,plot_volcano_color2,
     color.list = toxo@rdesc$species,
     color.name="Species",
     colors=c("Grey",brewer.pal(n=3,name = "Set2")[1:2]))

map2(results$contrasts,results$data,plot_volcano_color2,
     color.list = grepl("Nucleus",toxo@rdesc$subcellular.location),
     color.name="Nuclear",
     colors=c("Grey",brewer.pal(n=3,name = "Set2")[1:2]),
     alpha.list = case_when(grepl("Nucleus",toxo@rdesc$subcellular.location) ~ 1,
     		       TRUE ~ 0.005))

results.ratio <- results.ratio %>% mutate(
	turborah.vs.turbocyto.zscore = scale(turborah.vs.turbocyto.logFC),
	turborah.toxo.vs.mock.zscore = scale(turborah.toxo.vs.mock.logFC),
	turborah.toxo.vs.ctrl.zscore = scale(turborah.toxo.vs.ctrl.logFC),
	turbocyto.toxo.vs.ctrl.zscore = scale(turbocyto.toxo.vs.ctrl.logFC)
)

```

Write output to local directory
```{r }
write_output <- F

if(write_output){
	out <- left_join(results.ratio,toxo@rdesc)
	write_csv(out,"toxoplasma.tmt11.results.csv")

	
}

```

##5.1 Volcano plot showing mT-RAH+Toxo/mT-RAH+Toxo_no biotin
-show only Toxo proteins (filter by protein score >25 and protein coverage >1%, if appropriate)
-label known PV/PVM/exported proteins as one color
-label the 4 hypothetical Toxoplasma proteins as another color (green = PV validated, red = false positive)
```{r}
dat <- results$data[[3]] %>%
	left_join(toxo@rdesc) %>%
	filter(species == "Toxoplasma_gondii_GT1")  %>%
	mutate(label_novel = case_when(
		Location == "Novel PV/PVM" ~ str_extract(accession_number,"\\d+$"),
		T ~ ""
	))

g <- ggplot(dat,aes(x= logFC, y = -log10(P.Value),shape=species)) +
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat %>% filter(Location != "Unknown"),
		   mapping = aes(x=logFC,y=-log10(P.Value),color = Location))+
	scale_color_manual(values = toxo_colors)+
	geom_text_repel(dat, mapping = aes(x=logFC,y=-log10(P.Value),label = label_novel),
			nudge_y = 1,size=3)+
	labs(x = "log2 fold-change\n(mT-RAH+Toxo/mT-RAH+Toxo_no_biotin)", y = "-log10 p-value")+
	theme_bw()+
	scale_shape_manual(values=toxo_shapes)
g

dat <- results$data[[3]] %>%
	left_join(toxo@rdesc) %>%
	filter(species == "Toxoplasma_gondii_GT1")  %>%
	mutate(label_novel = case_when(
		Location == "Novel PV/PVM" ~ str_extract(accession_number,"\\d+$"),
		T ~ ""
	))


dat <- dat %>% mutate(gold_list = case_when(
		Location == "Exported" ~ "Exported",
		Location == "PV/PVM" ~ "PV/PVM",
		#lopit_prediction %in% c("19S proteasome","40S ribosome","60S ribosome") ~ "",
		!is.na(lopit_prediction) ~ "Non-secreted",
		T ~ ""
	))
g2 <- ggplot(dat,aes(x= logFC, y = -log10(P.Value),shape=species)) +
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat %>% filter(gold_list ==  "Non-secreted"),
		   mapping = aes(x=logFC,y=-log10(P.Value),color = gold_list))+
	geom_point(dat %>% filter(gold_list != "" & gold_list != "Non-secreted"),
		   mapping = aes(x=logFC,y=-log10(P.Value),color = gold_list))+
	scale_color_manual(values = toxo_colors)+
	labs(x = "log2 fold-change\n(mT-RAH+Toxo/mT-RAH+Toxo_no_biotin)", y = "-log10 p-value", color = "")+
	theme_bw()+
	scale_shape_manual(values=toxo_shapes)
g2
```
```{r}
pdf("./Figures/RAH-Toxo_vs_Nobiotin_Toxoplasma_Only.pdf",4.5,2.5)
g
g2
graphics.off()
```


##5.2  Volcano plot showing mT-RAH+Toxo/mT-RAH+mock
-show only human proteins (filter by protein score >25 and protein coverage >1%, if appropriate)
-label the 4 validated human proteins in another color

```{r}
dat <- results$data[[2]] %>%
	left_join(toxo@rdesc) %>%
	filter(species == "HUMAN")  %>%
	mutate(label_novel = case_when(
		Location == "Novel PV/PVM" ~ gene,
		T ~ ""
	))

g <- ggplot(dat,aes(x= logFC, y = -log10(P.Value))) +
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat %>% filter(Location != "Unknown"),
		   mapping = aes(x=logFC,y=-log10(P.Value),color = Location))+
	scale_color_brewer(type="qual")+
	geom_text_repel(dat, mapping = aes(x=logFC,y=-log10(P.Value),label = label_novel),
			nudge_y = 1,size=3)+
	labs(x = "log2 fold-change\n(mT-RAH+Toxo Infected/Mock)", y = "-log10 p-value")+
	theme_bw()
g
```
```{r}
pdf("./Figures/RAH-Toxo_Infected_vs_Mock_Host_Only.pdf",4,2.5)
g
graphics.off()
```


-Show only pathogen proteins
```{r}
dat <- results$data[[2]] %>%
	left_join(toxo@rdesc) %>%
	filter(species == "Toxoplasma_gondii_GT1")  %>%
	mutate(label_novel = case_when(
		Location == "Novel PV/PVM" ~ str_extract(accession_number,"\\d+$"),
		T ~ ""
	))

g <- ggplot(dat,aes(x= logFC, y = -log10(P.Value))) +
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat %>% filter(Location != "Unknown"),
		   mapping = aes(x=logFC,y=-log10(P.Value),color = Location))+
	scale_color_brewer(type="qual")+
	geom_text_repel(dat, mapping = aes(x=logFC,y=-log10(P.Value),label = label_novel),
			nudge_y = 1,size=3)+
	labs(x = "log2 fold-change\n(mT-RAH+Toxo Infected/Mock)", y = "-log10 p-value")+
	theme_bw()
g


```
-Show Host and Pathogen proteins
```{r}
dat <- results$data[[2]] %>%
	left_join(toxo@rdesc) %>%
	filter(species != "UNIQUE")  %>%
	mutate(label_novel = case_when(
		Location == "Novel PV/PVM" ~ str_extract(accession_number,"\\d+$"),
		T ~ ""
	))%>% mutate(gold_list = case_when(
		Location == "Exported" ~ "Exported",
		Location == "PV/PVM" ~ "PV/PVM",
		#lopit_prediction %in% c("19S proteasome","40S ribosome","60S ribosome") ~ "",
		!is.na(lopit_prediction) ~ "Non-secreted",
		T ~ ""
	))

g <- ggplot(dat,aes(x= logFC, y = -log10(P.Value),shape = species)) +
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat %>% filter(gold_list != ""),
		   mapping = aes(x=logFC,y=-log10(P.Value),color = gold_list, shape = species))+
	scale_color_brewer(type="qual")+
	labs(x = "log2 fold-change\n(mT-RAH+Toxo Infected/Mock)", y = "-log10 p-value")+
	theme_bw()
g


```


##5.3 Volcano plot showing mT-RAH+Toxo/mT-Cyto+Toxo
```{r}
dat <- results$data[[1]] %>%
	left_join(toxo@rdesc) %>%
	filter(species == "Toxoplasma_gondii_GT1")  %>%
	mutate(label_novel = case_when(
		Location == "Novel PV/PVM" ~ str_extract(accession_number,"\\d+$"),
		T ~ ""
	))

g <- ggplot(dat,aes(x= logFC, y = -log10(P.Value))) +
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat %>% filter(Location != "Unknown"),
		   mapping = aes(x=logFC,y=-log10(P.Value),color = Location))+
	scale_color_brewer(type="qual")+
	geom_text_repel(dat, mapping = aes(x=logFC,y=-log10(P.Value),label = label_novel),
			nudge_y = 1,size=3)+
	labs(x = "log2 fold-change\n(mT-RAH+Toxo/mT-RAH+Toxo_no_biotin)", y = "-log10 p-value")+
	theme_bw()
g

dat <- results$data[[1]] %>%
	left_join(toxo@rdesc) %>%
	filter(species == "Toxoplasma_gondii_GT1")  %>%
	mutate(label_novel = case_when(
		Location == "Novel PV/PVM" ~ str_extract(accession_number,"\\d+$"),
		T ~ ""
	))


dat <- dat %>% mutate(gold_list = case_when(
		Location == "Exported" ~ "Exported",
		Location == "PV/PVM" ~ "PV/PVM",
		#lopit_prediction %in% c("19S proteasome","40S ribosome","60S ribosome") ~ "",
		!is.na(lopit_prediction) ~ "Non-secreted",
		T ~ ""
	))
g2 <- ggplot(dat,aes(x= logFC, y = -log10(P.Value))) +
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat %>% filter(gold_list != ""),
		   mapping = aes(x=logFC,y=-log10(P.Value),color = gold_list))+
	scale_color_brewer(type="qual")+
	labs(x = "log2 fold-change\n(mT-RAH+Toxo/mT-RAH+Toxo_no_biotin)", y = "-log10 p-value", color = "")+
	theme_bw()
g2
```

## 5.4 2-D enrichment plot for human proteins
-show human and pathogen
-label the 4 validated human proteins (PDCD6, MOSPD2, CC2D1A, PDCD6IP)
```{r}
dat <- results.ratio %>%
	left_join(toxo@rdesc) %>%
	#filter(species == "HUMAN")  %>%
	mutate(label_novel = case_when(
		Location == "Novel PV/PVM" & species == "Toxoplasma_gondii_GT1" ~ str_extract(accession_number,"\\d+$"),
		Location == "Novel PV/PVM" ~ gene,
		T ~ ""
	))

g1 <- ggplot(dat, aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,shape = species))+
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat %>% filter(Location != "Unknown"),
		   mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,color = Location))+
	scale_color_manual(values=toxo_colors)+
	geom_text_repel(dat, mapping = aes(x=turborah.vs.turbocyto.logFC,
					   y=turborah.toxo.vs.mock.logFC,label = label_novel),
			nudge_x = -2,nudge_y = -0.7,size=3)+
	labs(x = "log2 fold-change\n(mT-RAH/mT in Infected)", y = "log2 fold-change\n(mT-RAH Infected/Mock)")+
	theme_bw()+
	scale_shape_manual(values=c("HUMAN"=16,"Toxoplasma_gondii_GT1" = 17, "UNIQUE" = NA))

g1


#Plot z-scores instead of logFC
dat.scaled <- dat
dat.scaled$turborah.vs.turbocyto.logFC <- scale(dat.scaled$turborah.vs.turbocyto.logFC)
dat.scaled$turborah.toxo.vs.mock.logFC<- scale(dat.scaled$turborah.toxo.vs.mock.logFC)

g2 <- ggplot(dat.scaled, aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,shape = species))+
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat.scaled %>% filter(Location != "Unknown"),
		   mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,color = Location))+
	scale_color_manual(values=toxo_colors)+
	geom_text_repel(dat.scaled, mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,label = label_novel),
			nudge_y = 1,size=3)+
	labs(x = "z-score\n(mT-RAH/mT in Infected)", y = "z-score\n(mT-RAH Infected/Mock)")+
	theme_bw()+
	scale_shape_manual(values=c("HUMAN"=16,"Toxoplasma_gondii_GT1" = 17, "UNIQUE" = NA))

g2

#Plot without Novel PV/PVM
dat <- dat %>% mutate(gold_list = case_when(
		Location == "Exported" ~ "Exported",
		Location == "PV/PVM" ~ "PV/PVM",
		#lopit_prediction %in% c("19S proteasome","40S ribosome","60S ribosome") ~ "",
		!is.na(lopit_prediction) ~ "Non-secreted",
		T ~ ""
	))


g3 <- ggplot(dat, aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,shape = species))+
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat %>% filter(gold_list != ""),
		   mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,color = gold_list,shape=species))+
	scale_color_manual(values=toxo_colors)+
	labs(x = "log2 fold-change\n(mT-RAH/mT in Infected)", y = "log2 fold-change\n(mT-RAH Infected/Mock)")+
	theme_bw()+
	scale_shape_manual(values=toxo_shapes)+
	geom_vline(xintercept = -0.65,linetype="dotted")

g3
```

```{r}
pdf("./Figures/4a.2D_Plot_Host_and_Pathogens.pdf",5,2.5)
g1
g2
g3
graphics.off()
```

-show human proteins only (filter by protein score >25 and protein coverage >1%, if appropriate)
-label the 4 validated human proteins (PDCD6, MOSPD2, CC2D1A, PDCD6IP)
```{r}
dat <- results.ratio %>%
	left_join(toxo@rdesc) %>%
	filter(species == "HUMAN")  %>%
	mutate(label_novel = case_when(
		Location == "Novel PV/PVM" ~ gene,
		T ~ ""
	))

g3 <- ggplot(dat, aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,shape = species))+
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat %>% filter(Location != "Unknown"),
		   mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,color = Location))+
	scale_color_brewer(type="qual")+
	geom_text_repel(dat, mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,label = label_novel),
			nudge_y = 1,size=3)+
	labs(x = "log2 fold-change\n(mT-RAH/mT in Infected)", y = "log2 fold-change\n(mT-RAH Infected/Mock)")+
	theme_bw()+
	scale_shape_manual(values=c("HUMAN"=16,"Toxoplasma_gondii_GT1" = 17, "UNIQUE" = NA))

g3


#Plot z-scores instead of logFC
dat.scaled <- dat
dat.scaled$turborah.vs.turbocyto.logFC <- scale(dat.scaled$turborah.vs.turbocyto.logFC)
dat.scaled$turborah.toxo.vs.mock.logFC<- scale(dat.scaled$turborah.toxo.vs.mock.logFC)

g4 <- ggplot(dat.scaled, aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,shape = species))+
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat.scaled %>% filter(Location != "Unknown"),
		   mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,color = Location))+
	scale_color_brewer(type="qual")+
	geom_text_repel(dat.scaled, mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,label = label_novel),
			nudge_y = 1,size=3)+
	labs(x = "z-score\n(mT-RAH/mT in Infected)", y = "z-score\n(mT-RAH Infected/Mock)")+
	theme_bw()+
	scale_shape_manual(values=c("HUMAN"=16,"Toxoplasma_gondii_GT1" = 17, "UNIQUE" = NA))

g4
```

```{r}
pdf("./Figures/4b.2D_Plot_Host_Only.pdf",4,2.5)
g3
g4
graphics.off()
```


## 5.5 2-D enrichment plot for pathogen proteins
-show pathogen proteins only (filter by protein score >25 and protein coverage >1%, if appropriate)
```{r}
dat <- results.ratio %>%
	left_join(toxo@rdesc) %>%
	mutate(label_novel = case_when(
		Location == "Novel PV/PVM" ~ str_extract(accession_number,"\\d+$"),
		T ~ ""
	))

g1<- ggplot(dat %>% filter(species == "Toxoplasma_gondii_GT1"), aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC))+
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat %>% filter(Location != "Unknown"),
		   mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,color = Location))+
	scale_color_brewer(type="qual")+
	geom_text_repel(dat, mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,label = label_novel),
			nudge_y = 1,size=3)+
	labs(x = "log2 fold-change\n(mT-RAH/mT in Infected)", y = "log2 fold-change\n(mT-RAH Infected/Mock)")+
	theme_bw()

g1


#Plot z-scores instead of logFC
dat.scaled <- dat
dat.scaled$turborah.vs.turbocyto.logFC <- scale(dat.scaled$turborah.vs.turbocyto.logFC)
dat.scaled$turborah.toxo.vs.mock.logFC<- scale(dat.scaled$turborah.toxo.vs.mock.logFC)

g2<- ggplot(dat.scaled %>% filter(species == "Toxoplasma_gondii_GT1"), aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC))+
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat.scaled %>% filter(Location != "Unknown" & species == "Toxoplasma_gondii_GT1"),
		   mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,color = Location))+
	scale_color_brewer(type="qual")+
	geom_text_repel(dat.scaled %>% filter(Location != "Unknown" & species == "Toxoplasma_gondii_GT1"), 
			mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,label = label_novel),
			nudge_y = 1,size=3)+
	labs(x = "z-score\n(mT-RAH/mT in Infected)", y = "z-score\n(mT-RAH Infected/Mock)")+
	theme_bw()

g2


```

-y-axis mtRAH+Toxo/mT-RAH+Toxo_no_biotin
```{r, fig.height=2.5 ,fig.width=5}
dat <- results.ratio %>%
	left_join(toxo@rdesc) %>%
	mutate(label_novel = case_when(
		Location == "Novel PV/PVM" ~ str_extract(accession_number,"\\d+$"),
		T ~ ""
	))

g1<- ggplot(dat %>% filter(species == "Toxoplasma_gondii_GT1"), aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.ctrl.logFC))+
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat %>% filter(Location != "Unknown" & species == "Toxoplasma_gondii_GT1"),
		   mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.ctrl.logFC,color = Location))+
	scale_color_brewer(type="qual")+
	geom_text_repel(dat %>% filter(species == "Toxoplasma_gondii_GT1"), 
			mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.ctrl.logFC,label = label_novel),
			nudge_y = 1,size=3)+
	labs(x = "log2 fold-change\n(mT-RAH/mT in Infected)", y = "log2 fold-change\n(mT-RAH Infected/No Biotin)")+
	theme_bw()

g1


#Plot z-scores instead of logFC
dat.scaled <- dat
dat.scaled$turborah.vs.turbocyto.logFC <- scale(dat.scaled$turborah.vs.turbocyto.logFC)
dat.scaled$turborah.toxo.vs.ctrl.logFC<- scale(dat.scaled$turborah.toxo.vs.ctrl.logFC)

g2<- ggplot(dat.scaled %>% filter(species == "Toxoplasma_gondii_GT1"), aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.ctrl.logFC))+
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat.scaled %>% filter(Location != "Unknown" & species == "Toxoplasma_gondii_GT1"),
		   mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.ctrl.logFC,color = Location))+
	scale_color_brewer(type="qual")+
	geom_text_repel(dat.scaled %>% filter(Location != "Unknown" & species == "Toxoplasma_gondii_GT1"), 
			mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.ctrl.logFC,label = label_novel),
			nudge_y = 1,size=3)+
	labs(x = "z-score\n(mT-RAH/mT in Infected)", y = "z-score\n(mT-RAH Infected/No Biotin)")+
	theme_bw()

g2

g3<- ggplot(dat.scaled , aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.ctrl.logFC,shape = species))+
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat.scaled %>% filter(Location != "Unknown" ),
		   mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.ctrl.logFC,color = Location))+
	scale_color_brewer(type="qual")+
	geom_text_repel(dat.scaled %>% filter(Location != "Unknown"), 
			mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.ctrl.logFC,label = label_novel),
			nudge_y = 1,size=3)+
	labs(x = "z-score\n(mT-RAH/mT in Infected)", y = "z-score\n(mT-RAH Infected/No Biotin)")+
	theme_bw()

g3

# Non-secreted/expected secreted
#Plot without Novel PV/PVM
dat <- dat %>% mutate(gold_list = case_when(
		Location == "Exported" ~ "Exported",
		Location == "PV/PVM" ~ "PV/PVM",
		#lopit_prediction %in% c("19S proteasome","40S ribosome","60S ribosome") ~ "",
		!is.na(lopit_prediction) ~ "Non-secreted",
		T ~ ""
	))


g4 <- ggplot(dat %>% filter(species == "Toxoplasma_gondii_GT1"),
	     aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.ctrl.logFC,shape = species))+
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat %>% filter(gold_list != ""),
		   mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.ctrl.logFC,color = gold_list,shape=species))+
	scale_color_manual(values=toxo_colors)+
	labs(x = "log2 fold-change\n(mT-RAH/mT in Infected)", y = "log2 fold-change\n(mT-RAH Infected/No Biotin)")+
	theme_bw()+
	scale_shape_manual(values=toxo_shapes)+
	geom_vline(xintercept = -0.65,linetype="dotted")

g4
```

```{r}
pdf("./Figures/5.2D_Plot_Pathogen_Only.pdf",4,2.5)
g1
g2
graphics.off()
```

## 5.5 Other plots
```{r}
#Compare Turbo-RAH to Turbo-cyto
plot_correlations(results.ratio,"turborah.toxo.vs.ctrl.logFC","turborah.vs.turbocyto.logFC",
		  color.list=results.ratio$turborah.vs.turbocyto.Q.Value<0.05 &
		  		  	results.ratio$turborah.toxo.vs.ctrl.Q.Value<0.05)

plot_correlations(results.ratio,"turborah.toxo.vs.ctrl.logFC","turborah.vs.turbocyto.logFC",
		  color.list=toxo@rdesc$species,colors=c("Grey",brewer.pal(n=3,name = "Set2")[1:2]),
		  alpha.list = case_when(toxo@rdesc$species == "HUMAN" ~ 0.005,
     		       TRUE ~ 1))

#Compare Turbo-RAH to Turbo-cyto, but use turboCyto:ctrl ratio
plot_correlations(results.ratio,"turbocyto.toxo.vs.ctrl.logFC","turborah.vs.turbocyto.logFC",
		  color.list=toxo@rdesc$species,colors=c("Grey",brewer.pal(n=3,name = "Set2")[1:2]),
		  alpha.list = case_when(toxo@rdesc$species == "HUMAN" ~ 0.005,
     		       TRUE ~ 1))

#Compare Turbo-RAH in toxoplasma to mock
plot_correlations(results.ratio,"turborah.toxo.vs.ctrl.logFC","turborah.toxo.vs.mock.logFC",
		  color.list=toxo@rdesc$species,colors=c("Grey",brewer.pal(n=3,name = "Set2")[1:2]),
		  alpha.list = case_when(toxo@rdesc$species == "HUMAN" ~ 0.05,
     		       TRUE ~ 1))

#Compare Turbo-RAH in toxo and mock, as well as turbocyto
plot_correlations(results.ratio,"turborah.vs.turbocyto.logFC","turborah.toxo.vs.mock.logFC",
		  color.list=toxo@rdesc$species,colors=c("Grey",brewer.pal(n=3,name = "Set2")[1:2]),
		  alpha.list = case_when(toxo@rdesc$species == "HUMAN" ~ 0.05,
     		       TRUE ~ 1))
##High-confidence PVM localizers
plot_correlations(results.ratio,"turborah.vs.turbocyto.logFC","turborah.toxo.vs.mock.logFC",
		  color.list=results.ratio$turborah.vs.turbocyto.Q.Value<0.10 &
		  	results.ratio$turborah.toxo.vs.mock.Q.Value<0.10&
		  	results.ratio$turborah.toxo.vs.ctrl.logFC>0 &
		  	results.ratio$turborah.vs.turbocyto.logFC>0,
		  shape.list=case_when(toxo@rdesc$species == "HUMAN" ~ 16,
		  		     TRUE ~ 3)  )

##High-confidence PVM localizers and centrosome annotation

labels <- toxo@rdesc$gene
labels[!toxo@rdesc$id.nodash %in% c("O75396","I3NI02","O60499","Q9NZ43","E9PCW1","O15498","Q13190","O15155")] <- ""
plot_correlations(results.ratio,"turborah.vs.turbocyto.logFC","turborah.toxo.vs.mock.logFC",
		  color.list=toxo@rdesc$id.nodash %in%
		  	c("O75396","I3NI02","O60499","Q9NZ43","E9PCW1","O15498","Q13190","O15155"),
		  alpha.list = case_when(toxo@rdesc$id.nodash %in%
		  		       	c("O75396","I3NI02","O60499","Q9NZ43",
		  		       	  "E9PCW1","O15498","Q13190","O15155") ~ 1,
		  		       TRUE ~ 0.2),
		  labels = labels)


##Medium-confidence PVM localizers
plot_correlations(results.ratio,"turborah.vs.turbocyto.logFC","turborah.toxo.vs.mock.logFC",
		  color.list=results.ratio$turborah.vs.turbocyto.Q.Value<0.10 &
		  	results.ratio$turborah.toxo.vs.ctrl.logFC>0&
		  	results.ratio$turborah.vs.turbocyto.logFC>0,
		  shape.list=case_when(toxo@rdesc$species == "HUMAN" ~ 16,
		  		     TRUE ~ 3)  )

##SNARE interactions in vesicular transport
labels <- toxo@rdesc$gene
labels[!toxo@rdesc$id.nodash %in% c("O75396","I3NI02","O60499","Q9NZ43","E9PCW1","O15498","Q13190","O15155")] <- ""
plot_correlations(results.ratio,"turborah.vs.turbocyto.logFC","turborah.toxo.vs.mock.logFC",
		  color.list=toxo@rdesc$id.nodash %in%
		  	c("O75396","I3NI02","O60499","Q9NZ43","E9PCW1","O15498","Q13190","O15155"),
		  alpha.list = case_when(toxo@rdesc$id.nodash %in%
		  		       	c("O75396","I3NI02","O60499","Q9NZ43",
		  		       	  "E9PCW1","O15498","Q13190","O15155") ~ 1,
		  		       TRUE ~ 0.2),
		  labels = labels)

##Low-confidence PVM localizers or multiple localizations
plot_correlations(results.ratio,"turborah.vs.turbocyto.logFC","turborah.toxo.vs.mock.logFC",
		  color.list=results.ratio$turborah.vs.turbocyto.Q.Value>0.10 &
		  	results.ratio$turborah.vs.turbocyto.logFC>-0.5&
		  	results.ratio$turborah.toxo.vs.ctrl.logFC>0,
		  shape.list=case_when(toxo@rdesc$species == "HUMAN" ~ 16,
		  		     TRUE ~ 3)  )

#List of known PV-localizing host proteins
plot_correlations(results.ratio,"turborah.vs.turbocyto.logFC","turborah.toxo.vs.mock.logFC",
		  color.list=toxo@rdesc$id.nodash %in%
		  	c("Q8WUM4","O75340","Q9Y512"),
		  alpha.list = case_when(toxo@rdesc$id.nodash %in%
		  		       	c("Q8WUM4","O75340","Q9Y512") ~ 1,
		  		       TRUE ~ 0.2),
		  labels = labels)


plot_correlations(results.ratio,"turborah.vs.turbocyto.logFC","turborah.toxo.vs.mock.logFC",
		  color.list=toxo@rdesc$Location,
		  colors=c(brewer.pal(n=3,name = "Set2")[1:3],"Grey"),
		  alpha.list = case_when(toxo@rdesc$Location=="Unknown" ~ 0.005,
     		       TRUE ~ 1))

#Various organelles
for(i in c("Nucleus","Golgi","Mitochon","Centrosome","Lysoso")){
	g <- plot_correlations(results.ratio,"turborah.vs.turbocyto.logFC","turborah.toxo.vs.mock.logFC",
			  color.list=grepl(i,toxo@rdesc$subcellular.location,ignore.case=T),
			  colors=c("Grey",brewer.pal(n=3,name = "Set2")[2]),
			  alpha.list = case_when(grepl(i,toxo@rdesc$subcellular.location,ignore.case=T) ~ 0.8,
			  		       TRUE ~ 0.05),
			  color.name=i)
	plot(g)
}

significant <- results.ratio %>% filter(results.ratio$turborah.vs.turbocyto.logFC>0)
organelle.results <- data.frame(organelle = character(),
				p = numeric())
for(i in c("Nucleus","Golgi","Mitochon","Centrosome","Lysoso")){

	
	x <- grepl(i,significant$subcellular.location,ignore.case=T) %>% sum
	m <- grepl(i,toxo@rdesc$subcellular.location,ignore.case=T) %>% sum
	n <- (!grepl(i,toxo@rdesc$subcellular.location,ignore.case=T)) %>% sum
	k <- nrow(significant)
	res <- phyper(x,m,n,k,lower.tail=F)
	cat(x,m,n,k)
	organelle.results <- rbind(organelle.results,data.frame(organelle = i,
								p= res))
}


plot_correlations(results.ratio,"turborah.vs.turbocyto.logFC","turborah.toxo.vs.mock.logFC",
		  color.list=results.ratio$turborah.toxo.vs.all.Q.Value<0.05&
		  	results.ratio$turborah.toxo.vs.all.logFC>0)


labels <- results.ratios$id
labels[results.ratios$turboRotenone.v.emptyRotenone.Q.Value>0.05 &
       	results.ratios$turboCtrl.v.emptyCtrl.Q.Value>0.05] <- ""

plot_correlations(results.ratios,"turboRotenone.v.emptyRotenone.logFC","turboCtrl.v.emptyCtrl.logFC",
		  color.list=filter(results.ratios,turboRotenone.v.emptyRotenone.Q.Value<0.05 |
		  		  	turboCtrl.v.emptyCtrl.Q.Value<0.05)$id,
		  labels = labels)


```




# 6 ROC Analysis

## 6.1 turborah.vs.turbocyto.logFC
```{r}
dat <- results.ratio %>%
	left_join(toxo@rdesc) %>%
	filter(species == "Toxoplasma_gondii_GT1")  %>%
	mutate(gold_list = case_when(
		Location != "Unknown" ~ "Positive",
		!is.na(lopit_prediction) ~ "Negative",
		T ~ ""
	)) %>%
	filter(gold_list != "")

score <-  dat$turborah.vs.turbocyto.logFC
class <- dat$gold_list == "Positive"
roc_empirical <- rocit(score = score, class = class) 
measures <- plot(roc_empirical)
cat("Optimal point: ", measures$`optimal Youden Index point`["cutoff"],
    "\nAUC: ",measures$AUC)


g<- ggplot(results.ratio, aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC))+
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat,
		   mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,color = gold_list))+
	scale_color_brewer(type="qual")+
	labs(x = "log2 fold-change\n(mT-RAH/mT in Infected)", y = "log2 fold-change\n(mT-RAH Infected/Mock)")+
	theme_bw()

g
```

### 6.1.1 With adj. p-value threshold
```{r}
dat <- results.ratio %>%
	left_join(toxo@rdesc) %>%
	filter(species == "Toxoplasma_gondii_GT1")  %>%
	mutate(gold_list = case_when(
		Location != "Unknown" ~ "PV/PVM",
		!is.na(lopit_prediction) ~ "Non-secreted",
		T ~ ""
	)) %>%
	filter(gold_list != "") #%>%
	#filter(turborah.toxo.vs.mock.P.Value < 0.1)

score <-  dat$turborah.vs.turbocyto.logFC
class <- dat$gold_list == "PV/PVM"
roc_empirical <- rocit(score = score, class = class) 
measures <- plot(roc_empirical)
cat("Optimal point: ", measures$`optimal Youden Index point`["cutoff"],
    "\nAUC: ",measures$AUC)


g<- ggplot(results.ratio, aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC))+
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat,
		   mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,color = gold_list))+
	scale_color_manual(values=toxo_colors)+
	labs(x = "log2 fold-change\n(mT-RAH/mT in Infected)", y = "log2 fold-change\n(mT-RAH Infected/Mock)")+
	theme_bw()

g

g1 <- ggplot(mapping = aes(m= dat$turborah.vs.turbocyto.logFC, d = dat$gold_list == "PV/PVM"))+
	labs(x= "1-Specificity (FPR)", y = "Sensitivity (TPR)")+
	geom_roc(n.cuts = 15,labelsize=3)+
	theme_bw()
g1

g2 <- ggplot(dat, aes(turborah.vs.turbocyto.logFC,after_stat(density),color = gold_list))+
	geom_freqpoly(binwidth=0.25)+
	labs(x="log2 fold-change\n(mT-RAH/mT in Infected)")+
	scale_color_manual(values=toxo_colors)+
	theme_bw()+
	geom_vline(xintercept=-0.65,linetype="dotted")
g2
```

```{r}
pdf("./Figures/ROC_Analysis_Results.pdf",4,2.5)
g
g2
graphics.off()

pdf("./Figures/ROC_Analysis_Results_part2.pdf",3,2.5)
g1
graphics.off()
```

Write results with applied threshold criteria
```{r}
write_csv(results.ratio %>% 
	  	filter(turborah.vs.turbocyto.logFC > -0.63 & turborah.toxo.vs.mock.P.Value <0.1 & turborah.toxo.vs.ctrl.adj.P.Val < 0.1) %>%
	  	left_join(toxo@rdesc),
	  file= "toxoplasma.tmt11.results.with.filtering.stringent.csv")

write_csv(results.ratio %>% 
	  	filter(turborah.vs.turbocyto.logFC > -0.63 & turborah.toxo.vs.mock.logFC > 0.5 & turborah.toxo.vs.ctrl.adj.P.Val < 0.1) %>%
	  	left_join(toxo@rdesc),
	  file= "toxoplasma.tmt11.results.with.filtering.relaxed.csv")
```


## 6.2 turborah.toxo.vs.mock.logFC
```{r}
dat <- results.ratio %>%
	left_join(toxo@rdesc) %>%
	filter(species == "Toxoplasma_gondii_GT1")  %>%
	mutate(gold_list = case_when(
		Location != "Unknown" ~ "Positive",
		!is.na(lopit_prediction) ~ "Negative",
		T ~ ""
	)) %>%
	filter(gold_list != "")

score <-  dat$turborah.toxo.vs.mock.logFC
class <- dat$gold_list == "Positive"
roc_empirical <- rocit(score = score, class = class) 
measures <- plot(roc_empirical)
cat("Optimal point: ", measures$`optimal Youden Index point`["cutoff"],
    "\nAUC: ",measures$AUC)


g<- ggplot(results.ratio, aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC))+
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat,
		   mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,color = gold_list))+
	scale_color_brewer(type="qual")+
	labs(x = "log2 fold-change\n(mT-RAH/mT in Infected)", y = "log2 fold-change\n(mT-RAH Infected/Mock)")+
	theme_bw()

g
```

## 6.3 Combined
```{r}
dat <- results.ratio %>%
	left_join(toxo@rdesc) %>%
	filter(species == "Toxoplasma_gondii_GT1")  %>%
	mutate(gold_list = case_when(
		Location != "Unknown" ~ "Positive",
		!is.na(lopit_prediction) ~ "Negative",
		T ~ ""
	)) %>%
	filter(gold_list != "")

score <-  dat$turborah.toxo.vs.mock.logFC + dat$turborah.vs.turbocyto.logFC
class <- dat$gold_list == "Positive"
roc_empirical <- rocit(score = score, class = class) 
measures <- plot(roc_empirical)
cat("Optimal point: ", measures$`optimal Youden Index point`["cutoff"],
    "\nAUC: ",measures$AUC)


g<- ggplot(results.ratio, aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC))+
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat,
		   mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.mock.logFC,color = gold_list))+
	scale_color_brewer(type="qual")+
	labs(x = "log2 fold-change\n(mT-RAH/mT in Infected)", y = "log2 fold-change\n(mT-RAH Infected/Mock)")+
	theme_bw()+geom_abline(intercept = 0.79, slope = -1)

g
```


## 6.4 turborah.toxo.vs.ctrl.logFC
```{r, fig.width=4.5, fig.height=3}
dat <- results.ratio %>%
	left_join(toxo@rdesc) %>%
	filter(species == "Toxoplasma_gondii_GT1")  %>%
	mutate(gold_list = case_when(
		Location != "Unknown" ~ "Positive",
		!is.na(lopit_prediction) ~ "Negative",
		T ~ ""
	)) %>%
	filter(gold_list != "")

score <-  dat$turborah.toxo.vs.ctrl.logFC
class <- dat$gold_list == "Positive"
roc_empirical <- rocit(score = score, class = class) 
measures <- plot(roc_empirical)
cat("Optimal point: ", measures$`optimal Youden Index point`["cutoff"],
    "\nAUC: ",measures$AUC)


g<- ggplot(results.ratio %>%
	left_join(toxo@rdesc) %>%
	filter(species == "Toxoplasma_gondii_GT1"), aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.ctrl.logFC))+
	geom_point(color="gray",alpha=0.3)+
	geom_point(dat,
		   mapping = aes(x=turborah.vs.turbocyto.logFC,y=turborah.toxo.vs.ctrl.logFC,color = gold_list))+
	scale_color_brewer(type="qual")+
	labs(x = "log2 fold-change\n(mT-RAH/mT in Infected)", y = "log2 fold-change\n(mT-RAH Infected/No Biotin)")+
	geom_vline(xintercept = -0.65,linetype="dotted")+
	geom_hline(yintercept = 2.95,linetype="dotted")+
	theme_bw()

g

g1 <- ggplot(mapping = aes(m= dat$turborah.toxo.vs.ctrl.logFC, d = dat$gold_list == "Positive"))+
	labs(x= "1-Specificity (FPR)", y = "Sensitivity (TPR)")+
	geom_roc(n.cuts = 15,labelsize=3)+
	theme_bw()
g1
```


#7. Pathway enrichment analysis
```{r}
dat <- results.ratio %>%
	left_join(toxo@rdesc) %>%
	filter(species == "HUMAN" & 
	       	turborah.vs.turbocyto.logFC > -0.65 &
	       	turborah.toxo.vs.ctrl.adj.P.Val < 0.01 &
	       	turborah.toxo.vs.ctrl.logFC > 0) %>%
	arrange(desc(turborah.toxo.vs.mock.logFC)) %>%
	.[1:50,]

gp <- gost(dat$id.nodash)
gostplot(gp)


g.list <- list()
col.index <- 1
for(j in c("GO:BP","GO:CC")){
	x <- gp$result %>% filter(source==j) %>% arrange(desc(p_value)) %>% top_n(n=-10,wt=p_value) %>% distinct(term_name,.keep_all = T)
	g1 <- ggplot(x,aes(x=factor(term_name,levels=term_name),y=-log10(p_value)))+
		geom_col(fill=brewer.pal(5,"Dark2")[col.index])+labs(x=j)+
		coord_flip()+scale_y_continuous(limits=c(0,4))+theme_cowplot(12)
	
	g.list[[j]] <- g1
	
	col.index <- col.index + 1
}

plots <- plot_grid(plotlist = g.list, align = "v",ncol = 1)
plot(plot_grid(plots, ncol = 1, rel_heights = c(0.1, 1)))
  
```
```{r}
pdf("./Figures/gprofiler.pathway.analysis.results.pdf",5,5)
plot(plot_grid(plots, ncol = 1, rel_heights = c(0.1, 1)))
graphics.off()

write_tsv(dat,"Toxoplasma_Top50_Human_Candidates.tsv")
write_tsv(gp$result %>% select(source,term_id,term_name,p_value),"gprofiler_pathway_enrichment_Top50.tsv")
```

